Response to the defense feedback

### 2021-06-01 Chapter-1/Chapter-1.tex
Updates from Overleaf

A large portion of side-channel attacks is the joint result of the underlying computer architecture and the software stack.  One example is cache channel attacks. The CPU cache is a smaller but faster memory designed to bridge the gap of the access time between the main memory and CPU registers by storing copies of recently accessed data. Because software may access different memory addresses when it processes different input data, and the size of the cache is significantly smaller than the size of the main memory, the CPU may only find part of the data in the cache. Such differences can be reflected in the variance in the program execution time. Hence we have cache side-channel attacks.

Various countermeasures have been proposed to defend against side-channel attacks. Based on the above discussion, existing countermeasures can be further divided into two categories, the hardware-based method and the software-based method. Hardware-level solutions, such as reducing shared resources, oblivious RAM, and transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need to adopt new hardware features and change  today's modern complex computer systems, which are hard to adopt in reality. Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side-channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) in existing code base. For example, when we examine recent side-channel attacks, many of them exploit two kinds of code patterns: \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
\begin{figure}[h]
    \begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
int secret[32];
...
while(i>0){
    r = (r * r) % n;
    if(secret[--i] == 1)
        r = (r * x) % n;   
}
\end{lstlisting}
    \caption{Secret-dependent control-flow transfer}
    \label{fig:secret:cf}
\end{figure}

Secret-dependent control-flow transfers happen when the value of secret can affect which branch the code executes. Figure~\ref{fig:secret:cf} shows an example. Depending on the value of \textsf{secret}, the code may or may not execute line 6. An attacker can retrieve some information based on the execution control-flow.

@@

Secret-dependent data accesses happen when the value of the secret can affect which memory location the code reads or writes. Figure~\ref{fig:secret:da} shows an example. \textsf{FSb} is an array. Depending on the value of \textsf{secret}, the code may read or write different items in the array.

@@

To address Problem 2, we make the following contributions on quantifying side-channel leakages on a multiple trace attack:
\begin{itemize}
    \item We propose a novel method that can detect and analyze the effect of each side-channel leakage site automatically. Our analysis combines the information from both the source code and the run-time execution, which makes the method more effective in finding the leakages. By applying a chi-squared test, the method can find independent leakages. Attackers can combine multiple leakage sites to retrieve more information as well.
    \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity. We propose a method that can estimate the lower bound of information leakages. The theory can serve as the foundation of the future work on quantifying the information leakage based on the fuzzing.
    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and real-world applications such as OpenSSL, mbedTLS, Libgcrpyt, TinyDNN, and GTK. The results show that our tool can detect and quantify the side-channel leakages effectively. Moreover, the leakage reports given by the \ctool{} can help developers fix the reported vulnerabilities.
\end{itemize}

>>>>

A large portion of side-channel attacks is the joint result of the underlying computer architecture and the software stack.  One example is cache channel attacks. The CPU cache is a smaller but faster memory designed to bridge the gap of the access time between the main memory and CPU registers by storing copies of recently accessed data. Because the size of the cache is significantly smaller than the size of the main memory, the CPU may only find part of the data in the cache. Accessing data from the cache is faster than Accessing data from the main memory. Such differences can be reflected in the variance in the program execution time. Hence we have cache channel attacks.

Various countermeasures have been proposed to defend against side-channel attacks. Existing countermeasures can be divided into two categories, hardware-based methods and software-based methods. Hardware-level solutions, such as reducing shared resources, oblivious RAM, and transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need to adopt new hardware features and change  today's modern complex computer systems, which are hard to adopt in reality. Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side-channel vulnerabilities in existing software code base. For example, when we examine recent side-channel attacks, many of them exploit two kinds of code patterns: \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
\begin{figure}[h]
    \begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
int secret[32];
...
while(i>0){
    r = (r * r) % n;
    if(secret[--i] == 1)
        r = (r * x) % n;   
}
\end{lstlisting}
    \caption{Secret-dependent control-flow transfer}
    \label{fig:secret:cf}
\end{figure}

Secret-dependent control-flow transfers happen when the value of secret can affect which branch the code executes. Figure~\ref{fig:secret:cf} shows an example. Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6. An attacker can retrieve some information by observing the execution control-flow.

@@

Secret-dependent data accesses happen when values of secret data affect which memory location the code reads or writes. Figure~\ref{fig:secret:da} shows an example. \textsf{FSb} is an array. Depending on the value of \textsf{secret}, the code may read or write different items in the array.

@@

To address Problem 2, we make the following contributions on quantifying side-channel leakages on a multiple trace attack:
\begin{itemize}
    \item We propose a novel method that can detect and analyze the effect of each side-channel leakage site automatically. Our analysis combines the information from both the source code and the run-time execution, which makes the method more effective in finding the leakages. By applying a chi-squared test, the method can find independent leakages. Attackers can combine multiple leakage sites to retrieve more information as well.
    \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity. The theory can serve as the foundation of the future work on quantifying the information leakage based on the fuzzing.
    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and real-world applications such as OpenSSL, mbedTLS, Libgcrpyt, TinyDNN, and GTK. The results show that our tool can detect and quantify the side-channel leakages effectively. Moreover, the leakage reports given by the \ctool{} can help developers fix the reported vulnerabilities.
\end{itemize}
